---
title: "Root Insurance Company - Work Sample"
---

Libraries Used
```{r}
library(dplyr)
library(plyr)
```

Please format the timestamps if both CSV files to Short Date format. Reading of file - Please choose file - referral_promo_participants.csv first and then promo_referrals.csv file.

```{r}
ref_promo_participants <- read.csv(file.choose())
promo_referrals <- read.csv(file.choose())
data1 <- ref_promo_participants
data2 <- promo_referrals
data1$bucket_timestamp <- as.Date(data1$bucket_timestamp, format = "%m/%d/%Y")
data1$bucket <- as.character(data1$bucket)
bucketCount <- count(data1, 'bucket')
bucketCount
data3 <- data1[data1$bucket == "off",]
data1 <- data1[!(data1$bucket == "off"),]
```

Creation of promo_startdate and promo_enddate columns

```{r}
data1$promo_startdate <- data1$bucket_timestamp
data1$promo_startdate <- if_else(data1$bucket == "48hr", data1$promo_startdate + 2, data1$promo_startdate)
data1$promo_startdate <- if_else(data1$bucket == "168hr", data1$promo_startdate + 7, data1$promo_startdate)
data1$promo_enddate <- data1$promo_startdate + 30
data2$receiver_account_timestamp <- as.Date(data2$receiver_account_timestamp, format = "%m/%d/%Y")
data2$receiver_quote_timestamp <- as.Date(data2$receiver_quote_timestamp, format = "%m/%d/%Y")
data2$receiver_policy_timestamp <- as.Date(data2$receiver_policy_timestamp, format = "%m/%d/%Y")
```

Merging of data using "user_id" and "sender_user_id" columns

```{r}
data4 <- merge(data1, data2, by.x = "user_id", by.y = "sender_user_id")
data4$sender_earned_amount_in_dollars[is.na(data4$sender_earned_amount_in_dollars)] <- 0
data4$receiver_earned_amount_in_dollars[is.na(data4$receiver_earned_amount_in_dollars)] <- 0
data5 <- merge(data3, data2, by.x = "user_id", by.y = "sender_user_id")
data5$sender_earned_amount_in_dollars[is.na(data5$sender_earned_amount_in_dollars)] <- 0
data5$receiver_earned_amount_in_dollars[is.na(data5$receiver_earned_amount_in_dollars)] <- 0
```

Used in answering Question 1

```{r}
bucketCountPromoConverstion <- count(data4, 'bucket')
bucketCountPromoConverstion
bucketCountNoPromoConversion <- count(data5,'bucket')
bucketCountNoPromoConversion
```

Used in answering Question 2

```{r}
bucketPromoQuotePolicyConversion <- data4 %>% group_by(bucket,receiver_quote,receiver_policy) %>% tally()
bucketPromoQuotePolicyConversion
bucketNoPromoQuotePolicyConversion <- data5 %>% group_by(bucket,receiver_quote,receiver_policy) %>% tally()
bucketNoPromoQuotePolicyConversion
table1 <- as.data.frame(tapply(data4$receiver_account,list(data4$bucket,data4$sender_earned_amount_in_dollars,data4$receiver_quote),sum))
table1
table2 <- as.data.frame(tapply(data5$receiver_account,list(data5$bucket,data5$sender_earned_amount_in_dollars,data5$receiver_quote),sum))
table2
table3 <- as.data.frame(tapply(data4$receiver_quote,list(data4$bucket,data4$sender_earned_amount_in_dollars),sum))
table3 
table4 <- as.data.frame(tapply(data5$receiver_quote,list(data5$bucket,data5$sender_earned_amount_in_dollars),sum))
table4
table5 <- as.data.frame(tapply(data4$receiver_policy,list(data4$bucket,data4$sender_earned_amount_in_dollars),sum))
table5
table6 <- as.data.frame(tapply(data5$receiver_policy,list(data5$bucket,data5$sender_earned_amount_in_dollars),sum))
table6
```

Used in answering Question 3 

```{r}
table7 <- as.data.frame(tapply(data4$sender_earned_amount_in_dollars,list(data4$bucket,data4$receiver_earned_amount_in_dollars),sum))
table7
bucketPromoReferralCost <- data4 %>% group_by(bucket,sender_earned_amount_in_dollars,receiver_earned_amount_in_dollars) %>% tally()
bucketPromoReferralCost
table8 <- as.data.frame(tapply(data5$sender_earned_amount_in_dollars,list(data5$bucket,data5$receiver_earned_amount_in_dollars),sum))
table8
bucketNoPromoReferralCost <- data5 %>% group_by(bucket,sender_earned_amount_in_dollars,receiver_earned_amount_in_dollars) %>% tally()
bucketNoPromoReferralCost
```